\pkg{dataMaid}: your assistant for documenting supervised data quality screening in \proglang{R}

### 2018-04-26 latex/article_accept.tex
Fixes bug with factors with unused factor levels

On page 3, we see the contents for the three first variables. Here, we identify a prefixed white space in the last name entry for President Truman and we find that a dot was entered as a first name; this is a typical choice for coding missing values in e.g., Stata, and therefore, it is flagged as a potential miscoded missing value. The variable \code{orderOfPresidency} is not summarized, visualized or checked because it is categorical and contains unique values for each observation.

@@

\begin{Schunk}
\begin{Sinput}
R> toyChecks <- check(toyData)
R> foo <- function(x) {
+    any(sapply(x, function(y) y[["problem"]]))
+  }
R> sapply(toyChecks, foo)
\end{Sinput}
\begin{Soutput}
       pill      events      region      change          id 
       TRUE        TRUE        TRUE        TRUE        TRUE 
spotifysong 
      FALSE 
\end{Soutput}
\end{Schunk}

>>>>

On page 3, we see the contents for the three first variables. Here, we identify a prefixed white space in the last name entry for President Truman and we find that a dot was entered as a first name; this is a typical choice for coding missing values in e.g., \proglang{Stata}, and therefore, it is flagged as a potential miscoded missing value. The variable \code{orderOfPresidency} is not summarized, visualized or checked because it is categorical and contains unique values for each observation.

@@

\begin{Schunk}
\begin{Sinput}
R> toyChecks <- check(toyData)
R> foo <- function(x) {
+    any(sapply(x, function(y) y[["problem"]])) }
R> sapply(toyChecks, foo)
\end{Sinput}
\begin{Soutput}
       pill      events      region      change          id 
       TRUE        TRUE        TRUE        TRUE        TRUE 
spotifysong 
      FALSE 
\end{Soutput}
\end{Schunk}
